\section{Risk Assessment}
\label{sec:risk-assessment}

\begin{longtable}[ht]{ p{.2\textwidth} p{0.05\textwidth}  p{0.05\textwidth} p{0.05\textwidth} p{0.53\textwidth}}
  \toprule
  \textbf{Risk}
   & \textbf{Loss}
   & \textbf{Prob}
   & \textbf{Risk}
   & \textbf{Mitigation}
  %
  \\\midrule\midrule
  Difficulty with\newline blockchain\newline development
   & 2
   & 3
   & \cellcolor{orange!50} 6
   & I will seek advice from my supervisor about how to tackle certain problems and decide on any changes my project might need. I could also use online documentation or forums for support.
  %
  \x
  Personal illness
  & 3
  & 2
  & \cellcolor{orange!50} 6
  & Depending on the amount of lost time, I may ignore some of the SHOULD or COULD requirements.
  %
  \x
  Laptop damaged or lost
   & 3
   & 1
   & \cellcolor{green!30} 3
   & All work is stored using version control and periodic backups will be
  made and stored locally and in cloud storage. I have other devices that
  could be used to continue development.
  %
  \x
  The application is not finished
   & 2.5
   & 4
   & \cellcolor{red!30} 10
   & This project is quite large in scope and will require a significant effort to implement and test. Using Agile development~\cite{ilieva_analyses_2004}, I will incrementally increase the scope of the project and ensure I have a minimum viable application. 
   A cut off point will be used to finish my implementation regardless of progress to focus on final testing and the report write up.
  \\\bottomrule\bottomrule
  \caption{The risk assessment of this project}
  \label{tab:risk assessment}
\end{longtable}