
\section{P2P File Sharing}
\label{sec:lit-p2p}

Table~\ref{tab:lit-review-p2p} looks at various implementations of P2P file-sharing networks. Using the pros and cons of each will help me identify key considerations of my own implementation.

\small
\begin{longtable}{ p{0.15\textwidth} p{0.8\textwidth} }
  \toprule
  \textbf{System} & \textbf{Description of Solution}
  \\\midrule\midrule
  IPFS~\cite{benet_ipfs_2014}
  & IPFS is a set of protocols for transferring and organising data over a content-addressable, peer-to-peer network. IPFS is open source and has many different implementations, such as Estuary~\cite{noauthor_estuary_nodate-1} or Kubo~\cite{noauthor_ipfskubo_2023}.
  %
  \x
  Swarm~\cite{hartman_swarm_1999}
  & Swarm is a distributed storage solution linked with Ethereum that has many similarities with IPFS~\cite{pouwelse_bittorrent_2005}. It uses an incentive mechanism, Swap (Swarm Accounting Protocol), that keeps track of data sent and received by each node in the network and then the payment owed for their contribution.
  %
  \x
  BitTorrent~\cite{pouwelse_bittorrent_2005}
  & See Section~\ref{sec:bittorrent}.
  %
  \x
  AFS~\cite{morris_andrew_1986,howard_scale_1988}
  & The Andrew File System was a prototype distributed system by IBM and Carnegie-Mellon University in the 1980s that allowed users to access their files from any computer in the network.
  %
  \x
  Napster~\cite{saroiu_measurement_2001}
  & Napster uses a central cluster of servers that maintain an index of every file on the network and which users have a copy of it. Clients will query the cluster for this information and will choose peers based upon their bandwidth. This protocol is dependant on a central cluster existing and will not function properly without it.  
  %
  \x
  Gnutella~\cite{saroiu_measurement_2001}
  & In Gnutella, nodes form an overlay network and will discover other peers through \textit{ping-pong} messages, where any node that receives a \textit{ping} message will forward it to their neighbours and send a \textit{pong} message to the originator. 
  A user will flood a download request to their peers until they find a suitable peer to download off of. A network flood in a large network will result in a significant amount of congestion and and a large amount of \textit{pong} messages going to a single node results in a DDoS attack.
  \\\bottomrule\bottomrule
  \caption{Various global distributed file systems.}
  \label{tab:lit-review-p2p}
\end{longtable}
\normalsize

\noindent
Some of the common themes found include:

\begin{itemize}
  \item \textbf{Trust} Nodes are typically anonymous so users have to trust that the data they download isn't malicious.
  \item \textbf{Illegal Content} There are no measures in place to stop or prevent the distribution of illegal content across these networks.
  \item \textbf{Payment} None of these networks natively support payment and thus don't support the access control systems required for payment systems.
\end{itemize}

\newparagraph
It is clear that using blockchain in conjunction with these systems could mitigate a lot of their issues and thus a combination of these two ideas will be used for this project.