\subsection{Frontend \& Controller}

\subsubsection{Frontend}

This application will have a GUI \reqref{F-S2} \reqref{NF-S2} where users can interact with the platform and will need to include the following pages:

\begin{itemize}
  \item \textbf{Library} The user's collection of owned games, where they can view details of each game owned as well as manage their download status.
  \item \textbf{Store} Where user's can find new games that have been uploaded by other users and purchase them.
  \item \textbf{Upload} Where user's can fill in details about a new game and have it be processed and uploaded to the blockchain.
  \item \textbf{Downloads} Where user's can track all of their owngoing downloads.
  \item \textbf{Peers} Where users can manage their list of connected peers.
  \item \textbf{Help} A help page to describe the application and all of its functionality \reqref{NF-C2}
\end{itemize}


\subsubsection{Controller}

The Controller will be the interface functions used for communication between the frontend and backend. Each function should be used to trigger an action/process or fetch some data. Some example Controller functions will include:

\begin{itemize}
  \item \textbf{PurchaseGame} Purchase a game off of Ethereum and add the metadata to the user's library.
  \item \textbf{StartDownload} Create a download for one of the user's owned games and start looking for blocks of data for it.
  \item \textbf{UploadGame} Upload a game to Ethereum given a set of input parameters.
\end{itemize}