\subsection*{User Walkthrough 2}\label{app:acc-test}

Here we show an example of how user walkthrough 2 from Section~\ref{sec:acc-tests} is carried out. In this test, one peer \p{1} will download a piece of data \g{1} off of another peer \p{2}. Both peers will interact with the Sepolia test-net where appropriate and will communicate wirelessly in the same local network.

\begin{enumerate}
  \item \p{1} and \p{2} own game \g{1}.
  \newline\textit{This is a given and the steps to reach this aren't necessary for this test. For this run, \p{2} will upload the game and \p{1} will purchase it}

  \item \p{1} connects to \p{2}
  \newline\textit{\p{1} heads to the Peers page and enters in the details for \p{2} and hits connect. \p{1} and \p{2} form a TCP connection.}
  % TODO add a log snippet here
  
  \item \p{1} and \p{2} exchange Ethereum addresses.
  \newline\textit{The logs show us that both \p{1} and \p{2} send and receive a VALIDATE\_REQ and VALIDATE\_RES command and that an address was successfully retrieved.}
  
  \item \p{1} starts a download for \g{1}.
  \newline\textit{\p{1} hits the download button in the game's library entry. }

  \item \p{1} sends requests for blocks to \p{2}.
  \newline\textit{From the logs we can see \p{2} receives requests for data with the BLOCK command.}

  \item \p{2} queries the smart contract to verify that \p{1} owns \g{1}.
  \newline\textit{The logs that \p{2} makes a query to the smart contract and finds that \p{1} owns the game.}
  
  \item \p{2} will respond to \p{1} with the requested data.
  \newline\textit{The logs show \p{1} receiving SEND\_BLOCK responses from \p{2} with their requested data.}

  \item \p{1} will verify each block of data received using its hash.
  \newline\textit{The logs show that after receiving a block its contents are checked against its hash.}

  \item \p{1} will have a full download of \g{1}
  \newline\textit{Using the diff command, we can see that \g{1} has been downloaded by directly comparing the original and downloaded file.}
  
\end{enumerate}