
\section{Blockchain-Based Cloud Storage}

Blockchain technology can be leverage for large-scale, distributed cloud storage to allow data to be stored across the network and provide public and private storage. In table~\ref{tab:blockhain cloud storage}, I detail some examples of how blockchain has been used to create cloud storage platforms or supplement existing ones:
\x
One gap found when researching these solutions was that 

\begin{longtable}{ p{0.35\textwidth} p{0.6\textwidth} }
  \toprule
  \textbf{Paper} & \textbf{Description of Solution}
  \\\midrule\midrule
  Blockchain Based Data Integrity Verification in P2P Cloud Storage~\cite{yue_blockchain_2018}
  & This paper uses Merkle trees to help verify the integrity of data within a P2P blockchain cloud storage network as well as looking at how different structures of Merkle trees effect the performance of the system.
  %
  \x
  Deduplication with Blockchain for Secure Cloud Storage~\cite{li_deduplication_2018}
  & This paper describes a deduplication scheme that uses the blockchain to record storage information and distribute files to multiple servers. This is implemented as a set of smart contracts.
  %
  \x
  Block-secure: Blockchain based scheme for secure P2P cloud storage~\cite{li_block-secure_2018}
  & A distributed cloud system in which users divide their own data into encrypted chunks and upload those chunks randomly into the blockchain, P2P network. 
  %
  \x
  Blockchain-Based Medical Records Secure Storage and Medical Service Framework~\cite{chen_blockchain-based_2018}
  & Describes a secure and immutable storage scheme to manage personal medical records as well as a service framework to allow for the sharing of these records.
  %
  \x
  A Blockchain-Based Access Control System for Cloud Storage~\cite{sukhodolskiy_blockchain-based_2018}
  & This paper describes a method for using blockchain to facilitate the access control over a cloud storage system. The blockchain stores an immutable record of all `\textit{meaningful security events}', such as key generation, access policy, assignment, etc.
  %
  \x
  Cloud Data Provenance using IPFS and Blockchain Technology~\cite{hasan_cloud_2019}
  & Uses blockchain technology and IPFS to provide an efficient way to securely store provenance~\footnote{Provenance data are access logs of stored data that can trace the integrity of data and will contain private user information.} data such that it is out of reach of adversaries, but can be used to verify the integrity of data on a cloud storage system. 
  \\\bottomrule\bottomrule
  \caption{\textit{Examples of blockchain cloud storage systems~\cite{sharma_blockchain_2021} }}
  \label{tab:blockhain cloud storage}
\end{longtable}

