
\section{Digital Ownership on the Blockchain}

Digital ownership is important to this project as it can be used to prove who actually owns the game being distributed and allow that user to provide access rights to other users for access to it. Table~\ref{tab:digital-ownership} looks at how various projects have handled the digital ownership of goods.
\x
One main issue with digital ownership has and always will be piracy. Many papers talk about solutions to reduce it but this is typically at the expense of the user's ownership or rights to access it.

\begin{longtable}{ p{0.35\textwidth} p{0.6\textwidth} }
  \toprule
  \textbf{Paper} & \textbf{Description of Solution}
  \\\midrule\midrule
  A digital rights management system based on a scalable blockchain~\cite{garba_digital_2021}
  & This paper describes a DRM (Digital Rights Management) system that restricts access of online content to authorized users and uses digital watermarking to reclaim copyright ownership following a content leak. The motivation behind it comes from the idea that content is more valuable the less accessible it is.
  \x
  The Blockchain-based Digital Content Distribution System~\cite{kishigami_blockchain-based_2015}
  & This content distribution system gives full control over the access rights of content to the owner....
  \x
  Visibility and digital art: Blockchain as an ownership layer on the Internet~\cite{mcconaghy_visibility_2017}
  & This paper talks about how blockchain can enable the secure attribution, transfer and provenance of digital property, which allows for unique and valuable pieces of digital content. They also mention how machine learning can be used to show how and where pieces of content are being used on the internet.
  \x
  Non-Fungible Token (NFT): Overview, Evaluation, Opportunities and Challenges~\cite{wang_non-fungible_2021}
  & This paper looks at the NFT ecosystem, where an NFT is a unique piece of content that has value on the blockchain based upon its properties. These allow creators to easily prove the existence and ownership of digital assets and provide them with royalties for any future exchanges of it. NFTs are based on Ethereum and use smart contracts.
  \\\bottomrule
  \label{tab:digital-ownership}
\end{longtable}

