
\section{BitTorrent}\label{sec:bittorrent}

\paragraph*{Motivation}
Due to the typical size of video games, it is impractical for every user to have a copy of every game. Therefore, it is important that I understand how a popular example of a peer-to-peer P2P file sharing system works when data is fragmented across the network.

\newparagraph
BitTorrent~\cite{kaune_unraveling_2010, pouwelse_bittorrent_2005} is a protocol for sharing data across a distributed network\footnote{Popular implementations include BitTorrent Web~\cite{inc_bittorrent_nodate}, qBittorrent~\cite{noauthor_qbittorrent_nodate}, and µTorrent~\cite{inc_torrent_nodate}} and 
it was chosen here because of its popularity, being responsible for 3.35\% of global bandwidth~\cite{noauthor_application_nodate}. 
In BitTorrent, users barter for blocks of data from a network of peers in a tit-for-tat fashion, such that users with a high upload rate will also typically have a high download rate.

\subsection*{Key Ideas}

\paragraph*{Trackers}
A tracker server keeps track of which peers have what data, which of those peers are available at, and will provide network statistics to \textit{recommend} which peers to connect to first.

\paragraph*{Block Priority}
Users will download blocks from other peers using the following priority:
\begin{enumerate}
  \item \textbf{Strict Priority} Data is split into pieces and sub-pieces where pieces are ideally downloaded together.
  \item \textbf{Rarest First} Download the pieces that have the fewest copies on the network to boost availability.
  \item \textbf{As Soon As Possible} A user with no peers will try get a random piece quickly so they can contribute to the network. 
\end{enumerate}

\paragraph*{Hashing}
Hashing privdes a unique fingerprint of some data, which can be used to verify the integrity of it. As data is broken into pieces, invalid pieces can easily be fetched again without interfering with any other pieces.

\paragraph*{Optimistic Unchoking}
A peer will allocate a portion of their bandwidth for communicating with unknown peers. This will allow new users to join the network and be able to contribute without being ignored by most peers and it gives a way for existing peers to seek better peers.

\subsection*{Availability}\label{subsec:availability}

One of the most significant issues facing BitTorrent is the availability of torrents, where \textit{`38\% of torrents become unavailable in the first month'}~\cite{kaune_unraveling_2010} and that \textit{`the majority of users disconnect from the network within a few hours after the download has finished'}~\cite{pouwelse_bittorrent_2005}.
This paper~\cite{neglia_availability_2007} looks at how the use of multiple trackers for the same content and DHTs can be used to boost availability. 
However, good availability requires users to \textit{choose} to contribute and often the built-in incentives aren't enough to encourage users to contribute for a long period of time.
