\addcontentsline{toc}{section}{Statement of Originality}
\section*{Statement of Originality}

\begin{itemize}
  \item I have read and understood the \href{}{ECS Academic Integrity}
        information and the University's \href{}{Academic Integrity
        Guidance for Students}.
  \item I am aware that failure to act in accordance with the \href{}
        {Regulations Governing Academic Integrity} may lead to the
        imposition of penalties which, for the most serious cases, may 
        include termination of programme.
  \item I consent to the University copying and distributing any or all 
        of my work in any form and using third parties (who may be based 
        outside the EU/EEA) to verify whether my work contains plagiarised 
        material, and for quality assurance purposes.
\end{itemize}
\vspace{2mm}
\noindent\textbf{\textit{You must \underline{change the statements in the boxes} if 
you do not agree with them.}}
\x
\noindent We expect you to acknowledge all sources of information (e.g. ideas, algorithms, data) using
citations. You must also put quotation marks around any sections of text that you have copied
without paraphrasing. If any figures or tables have been taken or modified from another source,
you must explain this in the caption and cite the original source.

\begin{longtable}[ht]{ | p{\textwidth} | }
  \hline
  \textbf{ I have acknowledged all sources, and identified any content taken from elsewhere.}
  \\\hline
\end{longtable}

\noindent If you have used any code (e.g. open-source code), reference designs, or similar resources that
have been produced by anyone else, you must list them in the box below. In the report, you must
explain what was used and how it relates to the work you have done.

\begin{longtable}[ht]{ | p{\textwidth} | }
  \hline
  \textbf{In Table~\ref{tab:tools-soo}, I acknowledge all third-party libraries or languages used for this project. Sections~\ref{ch:impl} and~\ref{ch:testing} discusses what they were used for.}
  \\\hline
\end{longtable}

\begin{longtable}[ht]{ | l | l | l | }
  \hline
  Golang~\cite{noauthor_go_nodate}
  &  go-ipfs-api~\cite{noauthor_go-ipfs-api_2023}
  & go-ethereum~\cite{noauthor_go-ethereum_nodate}
  \\\hline
  Zap~\cite{noauthor_zap_2023}
  & Viper~\cite{noauthor_viper_nodate}
  & JavaScript~\cite{noauthor_nodejs_nodate}
  \\\hline
  Wails~\cite{noauthor_wails_nodate}
  & Vue.js v3~\cite{noauthor_vuejs_nodate}
  & Vue Router~\cite{noauthor_vue_nodate}
  \\\hline
  markdown-it~\cite{noauthor_markdown-it_2023}
  & Pinia~\cite{noauthor_pinia_nodate}
  & SASS~\cite{noauthor_sass_nodate}
  \\\hline
  \caption{Third-party libraries and languages used to code this project}
  \label{tab:tools-soo}
\end{longtable}

\noindent You can consult with module teaching staff/demonstrators, but you should not show anyone else
your work (this includes uploading your work to publicly-accessible repositories e.g. Github, unless
expressly permitted by the module leader), or help them to do theirs. For individual assignments,
we expect you to work on your own. For group assignments, we expect that you work only with
your allocated group. You must get permission in writing from the module teaching staff before
you seek outside assistance, e.g. a proofreading service, and declare it here.

\begin{longtable}[ht]{ | p{\textwidth} | }
  \hline
  \textbf{I did all the work myself, or with my allocated group, and have not helped anyone else.}
  \\
  \textbf{Smart contract code deployed to an Ethereum test-net can be decompiled by any user. My smart contract source code was uploaded to Etherscan~\cite{etherscanio_library_nodate} to strengthen my argument of correctness.}
  \\\hline
\end{longtable}

\noindent We expect that you have not fabricated, modified or distorted any data, evidence, references,
experimental results, or other material used or presented in the report. You must clearly describe
your experiments and how the results were obtained, and include all data, source code and/or
designs (either in the report, or submitted as a separate file) so that your results could be
reproduced. 
\vspace{4mm}
\begin{longtable}[ht]{ | p{\textwidth} | }
  \hline
  \textbf{The material in the report is genuine, and I have included all my data/code/designs. }
  \\\hline
\end{longtable}

\noindent We expect that you have not previously submitted any part of this work for another assessment.
You must get permission in writing from the module teaching staff before re-using any of your
previously submitted work for this assessment.

\begin{longtable}[ht]{ | p{\textwidth} | }
  \hline
  \textbf{I have not submitted any part of this work for another assessment.}
  \\\hline
\end{longtable}

\noindent If your work involved research/studies (including surveys) on human participants, their cells or
data, or on animals, you must have been granted ethical approval before the work was carried
out, and any experiments must have followed these requirements. You must give details of this in
the report, and list the ethical approval reference number(s) in the box below.

\begin{longtable}[ht]{ | p{\textwidth} | }
  \hline
  \textbf{My work did not involve human participants, their cells or data, or animals.}
  \\\hline
\end{longtable}