
\subsection{Stakeholders}

This section will consider the key stakeholders, how they relate to this project, and what their impact will be on it.

\newcommand{\primary}{\hspace*{\fill}PRIMARY\\}
\newcommand{\secondary}{\hspace*{\fill}SECONDARY\\}
\newcommand{\tertiary}{\hspace*{\fill}TERTIARY\\}

\paragraph{Game Developers}\primary
This group will upload games, and any subsequent updates, to the applications. Users will purchase access to their games and contribute to the distribution of it in return for some reward that could be provided by this group.
\x
They will be the ones providing the content for the platform and will ultimately determine its success as a popular game will be the determining factor for users joining this platform. 

\paragraph{Players}\primary
This group will use this application to downloaded and update their games off of. They may also contribute to the distribution of the games to other players for an incentive provided by the developers.
\x
This group will be responsible for the long-term success of the platform as they will be the ones sharing games to other users and purchasing content. 

\paragraph{Other Platforms}\secondary
This group consists of platforms like Steam or Epic Games, which serve as the main competitor to this application. It is likely that as more developers choose this application, this group will see a loss in revenue.
\x
A lot of the design choices and features will be based upon what these platforms provide as my users will expect similar functionality from my platform if they are going to consider using it. 
